An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2011-01-26 paper.tex
Minor typos and tex formatting changes.

It should be noted that although an MCMC who jump acceptance criterium obeys detailed balance (as the Metropolis-Hastings algorithm does) must eventually converge to the desired distribution, there is no way to guarantee convergence in a fixed number of steps or to test whether a chain has converged in a foolproof manner.  For example, MCMC chains can get stuck on local maxima, and if the autocorrelation length of the chain represents a substantial fraction of the total number of samples, the effective sample size may be too small to accurately represent the relative sizes of the modes in the PDF (however, see Section \ref{sec:examples} for one intriguing suggestion for remedying this issue).

>>>>

It should be noted that although an MCMC whose jump acceptance
criterium obeys detailed balance (as the Metropolis-Hastings algorithm
does) must eventually converge to the desired distribution, there is
no way to guarantee convergence in a fixed number of steps or to test
whether a chain has converged in a foolproof manner.  For example,
MCMC chains can get stuck on local maxima, producing an apparently
well-converged sampling of the PDF in the vicinity of the maximum; or,
if the chain visits a sequence of local maxima, moving rarely between
maxima, the autocorrelation length of the chain may represent a
substantial fraction of the total number of samples, resulting in an
effective sample size that is too small to accurately represent the
relative sizes of the modes in the PDF (however, see Section
\ref{sec:examples} for one intriguing suggestion for remedying this
issue).
